### 2021-02-15 paper/natastron/Publication/bblmethods.tex
references done fucking finally

\begin{thebibliography}{10}
\expandafter\ifx\csname url\endcsname\relax
\def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\providecommand{\bibinfo}[2]{#2}
\providecommand{\eprint}[2][]{\url{#2}}

\bibitem{handberg+lund2014}
\bibinfo{author}{Handberg, R.} \& \bibinfo{author}{Lund, M.~N.}
\newblock \bibinfo{title}{Automated preparation of {{Kepler}} time series of
  planet hosts for asteroseismic analysis}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{445}}, \bibinfo{pages}{2698--2709}
  (\bibinfo{year}{2014}).

\bibitem{garcia+2011}
\bibinfo{author}{Garc{\'i}a, R.~A.} \emph{et~al.}
\newblock \bibinfo{title}{Preparation of {{Kepler}} light curves for
  asteroseismic analyses}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{414}}, \bibinfo{pages}{L6--L10}
  (\bibinfo{year}{2011}).

@@

\bibitem{buchhave+latham2015}
\bibinfo{author}{Buchhave, L.~A.} \& \bibinfo{author}{Latham, D.~W.}
\newblock \bibinfo{title}{The {{Metallicities}} of {{Stars}} with and without
  {{Transiting Planets}}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{808}}, \bibinfo{pages}{187} (\bibinfo{year}{2015}).

\bibitem{astropycollaboration+2013}
\bibinfo{author}{{Astropy Collaboration}} \emph{et~al.}
\newblock \bibinfo{title}{Astropy: {{A}} community {{Python}} package for
  astronomy}.
\newblock \emph{\bibinfo{journal}{Astronomy and Astrophysics}}
  \textbf{\bibinfo{volume}{558}}, \bibinfo{pages}{A33} (\bibinfo{year}{2013}).

@@

\bibitem{tassoul1980}
\bibinfo{author}{Tassoul, M.}
\newblock \bibinfo{title}{Asymptotic approximations for stellar nonradial
  pulsations}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal Supplement Series}}
  \textbf{\bibinfo{volume}{43}}, \bibinfo{pages}{469} (\bibinfo{year}{1980}).

\bibitem{hogg+2010}
\bibinfo{author}{Hogg, D.~W.}, \bibinfo{author}{Bovy, J.} \&
  \bibinfo{author}{Lang, D.}
\newblock \bibinfo{title}{Data analysis recipes: {{Fitting}} a model to data}.
\newblock \emph{\bibinfo{journal}{ArXiv e-prints}}
  \bibinfo{pages}{arXiv:1008.4686} (\bibinfo{year}{2010}).

\bibitem{mazumdar+2014}
\bibinfo{author}{Mazumdar, A.} \emph{et~al.}
\newblock \bibinfo{title}{Measurement of acoustic glitches in solar-type stars
  from oscillation frequencies observed by {{Kepler}}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{782}}, \bibinfo{pages}{18} (\bibinfo{year}{2014}).
\newblock \eprint{1312.4907}.

@@

@@

\bibitem{gaiacollaboration+2018}
\bibinfo{author}{{Gaia Collaboration}} \emph{et~al.}
\newblock \bibinfo{title}{Gaia {{Data Release}} 2. {{Summary}} of the contents
  and survey properties}.
\newblock \emph{\bibinfo{journal}{ArXiv e-prints}}
  \bibinfo{pages}{arXiv:1804.09365} (\bibinfo{year}{2018}).

\bibitem{raghavan+2010}
\bibinfo{author}{Raghavan, D.} \emph{et~al.}
\newblock \bibinfo{title}{A {{Survey}} of {{Stellar Families}}:
  {{Multiplicity}} of {{Solar}}-type {{Stars}}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal Supplement Series}}
  \textbf{\bibinfo{volume}{190}}, \bibinfo{pages}{1--42}
  (\bibinfo{year}{2010}).

@@

\bibitem{seabold+perktold2010}
\bibinfo{author}{Seabold, S.} \& \bibinfo{author}{Perktold, J.}
\newblock \bibinfo{title}{Statsmodels: {{Econometric}} and {{Statistical
  Modeling}} with {{Python}}} \bibinfo{pages}{5} (\bibinfo{year}{2010}).

\bibitem{foreman-mackey+2013}
\bibinfo{author}{{Foreman-Mackey}, D.}, \bibinfo{author}{Hogg, D.~W.},
  \bibinfo{author}{Lang, D.} \& \bibinfo{author}{Goodman, J.}
\newblock \bibinfo{title}{Emcee: {{The MCMC Hammer}}}.
\newblock \emph{\bibinfo{journal}{Publications of the Astronomical Society of
  the Pacific}} \textbf{\bibinfo{volume}{125}}, \bibinfo{pages}{306--312}
  (\bibinfo{year}{2013}).
\newblock \eprint{1202.3665}.

>>>>

\begin{thebibliography}{99}
\makeatletter
\addtocounter{\@listctr}{51}
\makeatother
\expandafter\ifx\csname url\endcsname\relax
\def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\providecommand{\bibinfo}[2]{#2}
\providecommand{\eprint}[2][]{\url{#2}}

\bibitem{handberg+lund2014}
\bibinfo{author}{Handberg, R.} \& \bibinfo{author}{Lund, M.~N.}
\newblock \bibinfo{title}{Automated preparation of {{Kepler}} time series of
	planet hosts for asteroseismic analysis}.
\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
\textbf{\bibinfo{volume}{445}}, \bibinfo{pages}{2698--2709}
(\bibinfo{year}{2014}).

\bibitem{garcia+2011}
\bibinfo{author}{Garc{\'i}a, R.~A.} \emph{et~al.}
\newblock \bibinfo{title}{Preparation of {{Kepler}} light curves for
	asteroseismic analyses}.
\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
\textbf{\bibinfo{volume}{414}}, \bibinfo{pages}{L6--L10}
(\bibinfo{year}{2011}).

\bibitem{christensen-dalsgaard2008}
\bibinfo{author}{{Christensen-Dalsgaard}, J.}
\newblock \bibinfo{title}{{{ASTEC}}\textemdash the {{Aarhus STellar Evolution
			Code}}}.
\newblock \emph{\bibinfo{journal}{Astrophysics and Space Science}}
\textbf{\bibinfo{volume}{316}}, \bibinfo{pages}{13} (\bibinfo{year}{2008}).

@@

\bibitem{buchhave+latham2015}
\bibinfo{author}{Buchhave, L.~A.} \& \bibinfo{author}{Latham, D.~W.}
\newblock \bibinfo{title}{The {{Metallicities}} of {{Stars}} with and without
	{{Transiting Planets}}}.
\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
\textbf{\bibinfo{volume}{808}}, \bibinfo{pages}{187} (\bibinfo{year}{2015}).

\bibitem{astropycollaboration+2013}
\bibinfo{author}{{Astropy Collaboration}} \emph{et~al.}
\newblock \bibinfo{title}{Astropy: {{A}} community {{Python}} package for
	astronomy}.
\newblock \emph{\bibinfo{journal}{Astron. Astrophys.}}
\textbf{\bibinfo{volume}{558}}, \bibinfo{pages}{A33} (\bibinfo{year}{2013}).

\bibitem{astropycollaboration+2018}
\bibinfo{author}{{Astropy Collaboration}} \emph{et~al.}
\newblock \bibinfo{title}{The {{Astropy Project}}: {{Building}} an
	{{Open}}-science {{Project}} and {{Status}} of the v2.0 {{Core Package}}}.
\newblock \emph{\bibinfo{journal}{Astron. J.}} \textbf{\bibinfo{volume}{156}},
\bibinfo{pages}{123} (\bibinfo{year}{2018}).

\bibitem{ginsburg+2019}
\bibinfo{author}{Ginsburg, A.} \emph{et~al.}
\newblock \bibinfo{title}{Astroquery: {{An Astronomical Web}}-querying
	{{Package}} in {{Python}}}.
\newblock \emph{\bibinfo{journal}{Astron. J.}} \textbf{\bibinfo{volume}{157}},
\bibinfo{pages}{98} (\bibinfo{year}{2019}).

@@

\bibitem{tassoul1980}
\bibinfo{author}{Tassoul, M.}
\newblock \bibinfo{title}{Asymptotic approximations for stellar nonradial
	pulsations}.
\newblock \emph{\bibinfo{journal}{Astrophys. J. Supplement Series}}
\textbf{\bibinfo{volume}{43}}, \bibinfo{pages}{469} (\bibinfo{year}{1980}).

\bibitem{vrard+2016}
\bibinfo{author}{Vrard, M.}, \bibinfo{author}{Mosser, B.} \&
\bibinfo{author}{Samadi, R.}
\newblock \bibinfo{title}{Period spacings in red giants. {{II}}. {{Automated}}
	measurement}.
\newblock \emph{\bibinfo{journal}{Astron. Astrophys.}}
\textbf{\bibinfo{volume}{588}}, \bibinfo{pages}{A87} (\bibinfo{year}{2016}).

\bibitem{hogg+2010}
\bibinfo{author}{{Hogg}, D.~W.}, \bibinfo{author}{{Bovy}, J.} \&
\bibinfo{author}{{Lang}, D.}
\newblock \bibinfo{title}{{Data analysis recipes: Fitting a model to data}}.
\newblock \emph{\bibinfo{journal}{arXiv e-prints}}
\bibinfo{pages}{arXiv:1008.4686} (\bibinfo{year}{2010}).
\newblock \eprint{1008.4686}.

\bibitem{hall+2019}
\bibinfo{author}{Hall, O.~J.} \emph{et~al.}
\newblock \bibinfo{title}{Testing asteroseismology with {{Gaia DR2}}:
	{{Hierarchical}} models of the {{Red Clump}}}.
\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
\textbf{\bibinfo{volume}{486}}, \bibinfo{pages}{3569--3585}
(\bibinfo{year}{2019}).
\newblock \eprint{1904.07919}.

\bibitem{mazumdar+2014}
\bibinfo{author}{Mazumdar, A.} \emph{et~al.}
\newblock \bibinfo{title}{Measurement of acoustic glitches in solar-type stars
	from oscillation frequencies observed by {{Kepler}}}.
\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
\textbf{\bibinfo{volume}{782}}, \bibinfo{pages}{18} (\bibinfo{year}{2014}).
\newblock \eprint{1312.4907}.

@@

\bibitem{carpenter+2017}
\bibinfo{author}{Carpenter, B.} \emph{et~al.}
\newblock \bibinfo{title}{Stan: {{A Probabilistic Programming Language}}}.
\newblock \emph{\bibinfo{journal}{Journal of Statistical Software}}
\textbf{\bibinfo{volume}{76}}, \bibinfo{pages}{1--32} (\bibinfo{year}{2017}).

@@

\bibitem{thetheanodevelopmentteam+2016}
\bibinfo{author}{{The Theano Development Team}} \emph{et~al.}
\newblock \bibinfo{title}{{Theano: A Python framework for fast computation of
		mathematical expressions}}.
\newblock \emph{\bibinfo{journal}{arXiv e-prints}}
\bibinfo{pages}{arXiv:1605.02688} (\bibinfo{year}{2016}).
\newblock \eprint{1605.02688}.

\bibitem{gaiacollaboration+2018}
\bibinfo{author}{{Gaia Collaboration}} \emph{et~al.}
\newblock \bibinfo{title}{{Gaia Data Release 2. Summary of the contents and
		survey properties}}.
\newblock \emph{\bibinfo{journal}{Astron. Astrophys.}}
\textbf{\bibinfo{volume}{616}}, \bibinfo{pages}{A1} (\bibinfo{year}{2018}).
\newblock \eprint{1804.09365}.

\bibitem{raghavan+2010}
\bibinfo{author}{Raghavan, D.} \emph{et~al.}
\newblock \bibinfo{title}{A {{Survey}} of {{Stellar Families}}:
	{{Multiplicity}} of {{Solar}}-type {{Stars}}}.
\newblock \emph{\bibinfo{journal}{Astrophys. J. Supplement Series}}
\textbf{\bibinfo{volume}{190}}, \bibinfo{pages}{1--42}
(\bibinfo{year}{2010}).

@@

\bibitem{seabold+perktold2010}
\bibinfo{author}{Seabold, S.} \& \bibinfo{author}{Perktold, J.}
\newblock \bibinfo{title}{{S}tatsmodels: {E}conometric and {S}tatistical
	{M}odeling with {P}ython}.
\newblock In \bibinfo{editor}{{S}t\'efan van~der {W}alt} \&
\bibinfo{editor}{{J}arrod {M}illman} (eds.)
\emph{\bibinfo{booktitle}{{P}roceedings of the 9th {P}ython in {S}cience
		{C}onference}}, \bibinfo{pages}{92 -- 96} (\bibinfo{year}{2010}).

\bibitem{betancourt+girolami2013}
\bibinfo{author}{{Astrophys. J.}, M.~J.} \& \bibinfo{author}{{Girolami}, M.}
\newblock \bibinfo{title}{{Hamiltonian Monte Carlo for Hierarchical Models}}.
\newblock \emph{\bibinfo{journal}{arXiv e-prints}}
\bibinfo{pages}{arXiv:1312.0906} (\bibinfo{year}{2013}).
\newblock \eprint{1312.0906}.

\bibitem{foreman-mackey+2013}
\bibinfo{author}{{Foreman-Mackey}, D.}, \bibinfo{author}{Hogg, D.~W.},
\bibinfo{author}{Lang, D.} \& \bibinfo{author}{Goodman, J.}
\newblock \bibinfo{title}{Emcee: {{The MCMC Hammer}}}.
\newblock \emph{\bibinfo{journal}{Publ. Astron. Soc. Pacific}}
\textbf{\bibinfo{volume}{125}}, \bibinfo{pages}{306--312}
(\bibinfo{year}{2013}).
\newblock \eprint{1202.3665}.

\bibitem{foreman-mackey2016}
\bibinfo{author}{{Foreman-Mackey}, D.}
\newblock \bibinfo{title}{Corner.py: {{Scatterplot}} matrices in {{Python}}}.
\newblock \emph{\bibinfo{journal}{The Journal of Open Source Software}}
\textbf{\bibinfo{volume}{1}} (\bibinfo{year}{2016}).
